Causal Bandits: Learning Good Interventions via Causal Inference

### 2016-02-05 causal-bandit/icml-2015/discussion.tex
fixed typo
updates graph feedback para

\todof {This paragraph could be be clearer. These results are sub-optimal as they apply to adversarial case such that opponent can effectively choose m = N}
Exploiting the variance structure in this way seems necessary even in the parallel bandit case.
If instead we choose to use other graph feedback models we would require those with time varying graphs~\citep{Alon2015,Kocak2014}.
Results for these models give a cumulative regret of $\bigo{\sqrt{\bar{\alpha} T}}$ where $\bar{\alpha}$ is the average independence number of the time varying graphs.
On each round, the feedback graph over the $2N$ possible interventions over $N$ binary variables would connect the chosen intervention to the corresponding intervention for each of the other $N-1$ observed variables.
Unfortunately, in this case the resulting star graphs have an $\bar{\alpha} = N$ and so the cumulative regret bounds would improve over those obtained by ignoring the causal graph structure.

@@

\paragraph{Causal Models with Non-Observable Variables}
If we assume knowledge of the conditional \textit{interventional} distributions $P_a$ our analysis applies unchanged to the case of causal models with 
non-observable variables. For example, if we had access to a data set of \textit{experiments} in which the reward variable $Y$ was not 
available from which to build estimates of $P_a$. Some of the interventional distributions $P_a$ may be non-identifiable meaning we can not obtain prior estimates for $P_a$ from 
even an infinite amount of observational data. Even if all variables are observable and the graph is known, if the conditional distributions are unknown, then Algorithm
\ref{alg:general} cannot be used. Estimating these quantities will simultaneously minimising the simple regret is an interesting and challenging open problem.

>>>>

The parallel bandit problem can also be viewed as an instance of a time varying graph feedback problem \citep{Alon2015,Kocak2014}, where at each timestep the feedback graph $G_t$ is selected stochastically, dependent on $\boldsymbol{q}$, and revealed after an action has been chosen. The feedback graph is distinct from the causal graph. A link $A \rightarrow B$ in $G_t$ indicates that selecting the action $A$ reveals the reward for action $B$. For this parallel bandit problem, $G_t$ will always be a star graph with the action $do()$ connected to half the remaining actions. However, \citet{Alon2015,Kocak2014} give adversarial algorithms, which when applied to the parallel bandit problem obtain the standard bandit regret. A malicious adversary can select the same graph each time, such that the rewards for half the arms are never revealed by the informative action. This is equivalent to a, nominally, stochastic selection of feedback graph where $\boldsymbol{q} = \boldsymbol{0}$.

@@

\paragraph{Causal Models with Non-Observable Variables}
If we assume knowledge of the conditional \textit{interventional} distributions $P_a$ our analysis applies unchanged to the case of causal models with 
non-observable variables. For example, if we had access to a data set of \textit{experiments} in which the reward variable $Y$ was not 
available from which to build estimates of $P_a$. Some of the interventional distributions $P_a$ may be non-identifiable meaning we can not obtain prior estimates for $P_a$ from 
even an infinite amount of observational data. Even if all variables are observable and the graph is known, if the conditional distributions are unknown, then Algorithm
\ref{alg:general} cannot be used. Estimating these quantities while simultaneously minimising the simple regret is an interesting and challenging open problem.
